A generalized definition of multidimensional item response theory parameters

### 2022-11-10 output/paper_draft/paper_M2PLM_parameters.Rmd
WIP: Inner product matrix diagonal
Finishes Proposition 1 and proof

::: {#prp-cosines-equivalence}

@@

\begin{equation}
  `r DIR_COS_VEC_EQ`.                             (\#eq:direction-cosine-vector)
\end{equation}

@@

@@

By Equation \@ref(eq:inner-prod-matrix-def) it is clear that
$`r DIAG_INNER_PROD_MATRIX_EQ`$
(but note that the basis vectors are not necessarily unitary).
By defining $`r DIAG_MATRIX_INNER_PROD`$ as
the diagonal matrix with the same diagonal as $`r INNER_PROD_MATRIX`$,
Equation \@ref(eq:direction-cosine) in matrix notation is<!-- # TODO:
Not sure if it’s necessary to explain this further.
There may be a certain “inferential leap” assuming that D^(-1/2) is
the matrix form equivalent to 1/u_k,
(but I “know” intuitively that the generalization holds) -->

>>>>

::: {#prp-dir-cosines-generalized-basis}

@@

\begin{equation}
  `r DIR_COS_VEC_EQ`                              (\#eq:direction-cosine-vector)
\end{equation}

@@

\begin{equation}
  `r DIAG_MATRIX_INNER_PROD_EQ`.
\end{equation}

Therefore,

::: {.proof}
*Proof.*

For every $`r DIM_INDEX`$; $`r DIM_ENUM_EQ`$,

\begin{equation}
  `r DIR_COSINE_PROOF_EQ`,                        (\#eq:dir-cosine-proof-prop-1)
\end{equation}

with $`r INNER_PROD_MATRIX_ROW`$ the $`r DIM_INDEX`$-th row of
$`r INNER_PROD_MATRIX`$.

Therefore, $`r DIR_COS_VEC_EQ`$ and $`r TRAIT_VECTOR_POLAR_EQ`$.
$`r END_OF_PROOF`$
:::

@@
